R for Clinical Study Reports and Submission

### 2021-08-29 tlf-efficacy.Rmd
flx typo: tlf-efficacy

We first define the analysis dataset using 
efficacy population flag `EFFFL` and 
all records post baseline (`AVISITN > 1`) and on or before Week 24 (`AVISITN <= 12`).

>>>>

We first define the analysis dataset using 
efficacy population flag `EFFFL` and 
all records post baseline (`AVISITN > 1`) and on or before Week 24 (`AVISITN <= 24`).
